Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-29 paper/competing_bandits.tex
fix weird bib issue and add additional citation

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system
    \cite{Frazier-ec14,Kremer-JPE14,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    \cite{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
pay-per-click ad auctions 
    \cite{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.

\OMIT{ %%%%%%
The interplay between exploration, exploitation, and incentives has been studied in several other settings, the most relevant to this paper being \citealt*{che2017recommender}, \citealt*{kremer2014implementing}, \citealt*{mansour2015bayesian}. The strategic experimentation literature in economics, such as \citealt*{bolton1999strategic} and \citealt*{keller2005strategic}, studies models with self-interested agents jointly performing exploration whereas in this paper the firms cannot observe the actions or the payoffs of the other firms and exploration is coordinated by the consumers.
} %%%%%%%%

@@

An alternative interpretation of the results in the previous section is that the "temporary monopoly" provides a first mover advantage to the incumbent firm and that this first mover advantage allows the firm to both get a data advantage as well as a reputational advantage over the entrant. This provides an alternative interpretation of the classic "first mover advantage" that has been well-studied in economics and marketing \cite*{kerin1992first} where, in our model, an incumbent can use data and reputation as a barrier to entry simply due to the fact that they were in the market before the entrant. Which plays a bigger role in preventing the entrant from being able to establish market share? We run two additional experiments, modifying the previous temporary monopoly experiment so that in one experiment the reputation of the incumbent is artificially erased (Reputation Erased Experiment) and another in which the information gained by the incumbent is artificially erased so that the posterior is reset to the prior (Information Erased Experiment).

>>>>

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system
    \cite{Frazier-ec14,Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    \cite{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
pay-per-click ad auctions 
    \cite{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.

\OMIT{ %%%%%%
The interplay between exploration, exploitation, and incentives has been studied in several other settings, the most relevant to this paper being \cite{che2017recommender}, \cite{kremer2014implementing}, \cite{mansour2015bayesian}. The strategic experimentation literature in economics, such as \cite{bolton1999strategic} and \cite{keller2005strategic}, studies models with self-interested agents jointly performing exploration whereas in this paper the firms cannot observe the actions or the payoffs of the other firms and exploration is coordinated by the consumers.
} %%%%%%%%

@@

An alternative interpretation of the results in the previous section is that the "temporary monopoly" provides a first mover advantage to the incumbent firm and that this first mover advantage allows the firm to both get a data advantage as well as a reputational advantage over the entrant. This provides an alternative interpretation of the classic "first mover advantage" that has been well-studied in economics and marketing \cite{kerin1992first} where, in our model, an incumbent can use data and reputation as a barrier to entry simply due to the fact that they were in the market before the entrant. Which plays a bigger role in preventing the entrant from being able to establish market share? We run two additional experiments, modifying the previous temporary monopoly experiment so that in one experiment the reputation of the incumbent is artificially erased (Reputation Erased Experiment) and another in which the information gained by the incumbent is artificially erased so that the posterior is reset to the prior (Information Erased Experiment).
